AIMS Data Platform R Client Notebook Example

### 2019-09-03 docs/detailed-example.Rmd
Fix typo

Variable  | Value                  | Description
----------|------------------------|-------------------------------------------------------
dio       | 10.25845/5c09bf93f315d | DOI for AIMS Weather found [here](https://aims.github.io/data-platform)
series    | 64                     | Found [here](https://aims.github.io/data-platform/weather/series), Davies Reef Air Temperature data series
from-date | '2018-01-01'           | We want to start charting on 1/1/2018
thru-date | '2018-01-10'           | We are plotting 10 days of data

>>>>

Variable  | Value                  | Description
----------|------------------------|-------------------------------------------------------
doi       | 10.25845/5c09bf93f315d | DOI for AIMS Weather found [here](https://aims.github.io/data-platform)
series    | 64                     | Found [here](https://aims.github.io/data-platform/weather/series), Davies Reef Air Temperature data series
from-date | '2018-01-01'           | We want to start charting on 1/1/2018
thru-date | '2018-01-10'           | We are plotting 10 days of data
